### 2014-05-13 reports/report.Rmd
Add reports. Closes #93

```{r, echo=FALSE}

locLevelInfo  <-  function(data){

  vars <- c("location","longitude","latitude","vegetation")

  loc <- data[!duplicated(data[,vars]),vars]

  loc[is.na(loc) | loc=="" | loc=="NA"]  <-  "missing"  
  return(loc)
}

standLevelInfo  <-  function(data){

  vars <- c("location","grouping","growingCondition") #,"status")
  sta <- data[!duplicated(data[,vars]),vars]

  if(all(is.na(sta$grouping)))
    sta  <-  sta[,-which(names(sta) == "grouping")]

  sta[is.na(sta) | sta=="" | sta=="NA"]  <-  "missing"

  return(sta)
}

spLevelInfo  <-  function(data){
  spec         <-  data.frame(species=as.character(unique(data$species)), stringsAsFactors=FALSE)
  for(z in c("family", "pft")){
    spec[[z]]  <-  as.character(data[[z]][match(spec$species,data$species)])
    i          <-  spec[[z]]=="" | is.na(spec[[z]]) 
    if(any(i)){
      spec[[z]][i]  <-  "missing"
    }
  }
  j            <-  spec$species=="" | is.na(spec$species) 
  if(any(j)){
    spec$species[j]  <-  "missing"
  }
  spec
}

printMeta  <-  function(data){
  dataset   <-  as.character(unique(data$dataset))
  openMeta  <-  read.csv(paste0("../",mashrDetail("dir.raw"),"/",dataset,"/studyMetadata.csv"), h=TRUE, stringsAsFactors=FALSE)
  openMeta
}

```

@@

## Citation
Information about the primary reference for the data you provided. 
```{r echo=FALSE, comment=''}
  bibfile<- paste0("../", as.character(.dat$ref$filename))
```
**Reference:** `r formatBib(bibfile)[[1]]`

**DOI:** `r  bibGetElement(bibfile, element = "doi")`

**Abstract:** `r  bibGetElement(bibfile, element = "abstract")`

@@

```{r echo=FALSE, comment=''}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%mashrDetail("var.def")$Variable[mashrDetail("var.def")$Group=="tree"]]
cbind(counts)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
standLevelInfo(.dat$data)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
spLevelInfo(.dat$data)
```

### Methods
```{r echo=FALSE, message=FALSE, warning=FALSE, comment=''}
metaTable  <-  printMeta(.dat$data)
for(j in 1:nrow(metaTable)){
  cat(paste0(metaTable[j,1], ": ", metaTable[j,2], "\n\n"))
}

```

@@

```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata$data, .study, pdf=FALSE, quiet=TRUE)
```

>>>>

```{r, echo=FALSE}
source('report-fun.R')
```

@@

## Citation
Information about the primary reference for the data you provided.

**Reference:** `r .dat$references$citation`

**DOI:** `r  bibGetElement(.dat$bib, element = "doi")`

**Abstract:** `r  bibGetElement(.dat$bib, element = "abstract")`

@@

```{r echo=FALSE, comment=''}
counts  <-  apply(!is.na(.dat$data), MARGIN=2, FUN = sum)
counts  <-  counts[counts>0]  #only include no zeros
counts  <-  counts[names(counts)%in%.dat$dictionary$Variable[.dat$dictionary$Group=="tree"]]
cbind(counts)
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
kable(standLevelInfo(.dat$data))
```

@@

```{r echo=FALSE, message=FALSE, warning=FALSE, comment='',results="asis"}
kable(spLevelInfo(.dat$data))
```

### Methods
```{r echo=FALSE, message=FALSE, warning=FALSE, comment='', results="asis"}
metaTable  <-  getMeta(.study)
writeLines(paste0(metaTable[,1], ": ", metaTable[,2], "\n"))
```

@@

```{r fig.height=8, fig.width=8, echo=FALSE, warning=FALSE, message=FALSE}
makePlotPanel(alldata, .dat)
```
